---
title: "LMAs and Stroma (IROC)"
author: "Karanvir Singh"
date: "2023-05-01"
format:
  html:
    code-fold: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)

library(tidyverse)
library(cowplot)
library(ggpubr)
source("/Users/karanvir/Documents/LMAProject/COEUR/Scripts/Neighborhood Analysis/SPIAT_functions.R")
```

## Figure 1 - LMA barplots

```{r}
lma <- vroom::vroom("/Users/karanvir/Documents/LMAProject/IROC_TMA/Results/Neighborhood-analysis/7LMAs_15r15n_IROC_TMA.csv")

colnames(lma) <- gsub("CD20p" , "CD79ApCD20p", colnames(lma)) %>%
  gsub("^PD1p$", "CD3nCD8nPD1p", .)

getClusterPlots(lma, breaks = c("CD3pCD8nPD1p", "CD3pCD8nPD1n", "CD3pCD8pPD1p", "CD3pCD8pPD1n", "CD68pPDL1n", 
"CD68pPDL1p", "CD79ApCD20p", "CD79ApCD20n",  "CD3nCD8nPD1p"), cell_type_colors = c("#E64B35FF",
                                                                                   "#f5b8af",
                                                                                   "#358295",
                                                                                   "#a6ddea",
                                                                                   "green",
                                                                                   "yellow",
                                                                                   "#744960",
                                                                                   "#d4a2bc",
                                                                                   "black"))
```

## Figure 2: Number of cases by stroma percentage

There are 60 cores with neighborhoods detected, out of 137 images stained. The median stroma proportion is 38% - cases with more stroma than these are catagorizes as 'high', lower as 'low'.

The total number of LMAs detected is quite similar between high and low stroma cases, however the distribution by LMA subtype is different. There are more LMA5/6/7 in low stroma cores (these are the LMAs with more PDL1p macs). LMA1/2/3 are found in high stroma cores more often (these are the LMAs with more PDL1- macs).

```{r}
densities <- vroom::vroom("/Users/karanvir/Documents/LMAProject/IROC_TMA/Results/IROC-tma-per-patient-densities.csv")
counts <- vroom::vroom("/Users/karanvir/Documents/LMAProject/IROC_TMA/Results/IROC-tma-per-image-counts.csv")

lma <- left_join(lma, counts %>% select(Image, ID))
lma <- left_join(lma, densities %>% select(ID, stroma_proportion))
lma <-  mutate(lma, stroma_cat = case_when(stroma_proportion <= median(stroma_proportion) ~ "low",
                                           TRUE ~ "high"))

stroma_tally <- lma %>% group_by(ID, LMA, stroma_cat) %>% summarise(numberOfLMAs = n()) %>%
  group_by(stroma_cat, LMA) %>% summarise(sumLMAs = sum(numberOfLMAs))


stroma_tally %>% 
  ggplot(aes(x=stroma_cat, y=sumLMAs)) +
  geom_col(position=position_dodge())+
  xlab("Stroma category")+
  ylab("Nunber of LMAs")+
  ggtitle("Fig. 2: Total number of neighborhoods detected by stroma %")

stroma_tally %>% 
  ggplot(aes(x=stroma_cat, y=sumLMAs)) +
  geom_col(position=position_dodge())+
  facet_wrap(~LMA, nrow=1)+
  xlab("Stroma category")+
  ylab("Nunber of LMAs")+
  ggtitle("Fig. 3: Total number of neighborhoods detected by stroma % and LMA type")
```
