---
title: "COEUR BT and ADAPT LMAs Analysis"
author: "Karanvir Singh"
date: "2023-04-11"
format:
  html:
    code-fold: true
    
project:
  type: default
  execute-dir: project
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
library(tidyverse)
library(ggsci)
library(cowplot)
library(ggpubr)
library(rstatix)
```

I have identified neighborhood in each image stained with the BT and ADAPT panel from the COEUR TMAs. I need to import this cell level data, filter for the cases that we are using in the heatmap (have survival analysis, samples are pre-treatment).

# Pre-processing

## Importing .RData files from the SPIAT workflow

```{r import}
load("/Users/karanvir/Documents/LMAProject/COEUR/Results/Spatial Analysis/RData/BT_15r_15n_SPIAT.RData")
btNeighborhoods <- neighborhoods
load("/Users/karanvir/Documents/LMAProject/COEUR/Results/Spatial Analysis/RData/ADAPT_15r_15n_SPIAT.RData")
adaptNeighborhoods <- neighborhoods
rm(neighborhoods)

stroma_information<- read.csv("../../../Final_Data/COMBINED_PANELS_DENSITIES_08NOV22.csv") %>%
  select(pNum, avg_epi_prop)



```

## Collapse list into one dataframe

```{r}
btNeighborhoods <- bind_rows(btNeighborhoods, .id="Image")
adaptNeighborhoods <- bind_rows(adaptNeighborhoods, .id="Image")
```

## Filter for patients used in TME clustering and survival analysis

```{r, message=FALSE}
harmonizedCounts <- vroom::vroom("/Users/karanvir/Documents/LMAProject/COEUR/Final_Data/COMBINED_PANELS_DENSITIES_08NOV22.csv")
countsbt <- vroom::vroom("/Users/karanvir/Documents/LMAProject/COEUR/Final_Data/BT_per_image_counts.csv")
countsadapt <- vroom::vroom("/Users/karanvir/Documents/LMAProject/COEUR/Final_Data/ADAPT_per_image_counts.csv")
tme <- vroom::vroom("../../Clustering/TME_pNum_key.txt")

# Adding patient identified to the cell level data
btNeighborhoods <- left_join(btNeighborhoods, countsbt %>% select(Image, pNum))
adaptNeighborhoods <- left_join(adaptNeighborhoods, countsadapt %>% select(Image, pNum))

# Filter for pNums with TME data
btNeighborhoods <- filter(btNeighborhoods, pNum %in% tme$pNum)
adaptNeighborhoods <- filter(adaptNeighborhoods, pNum %in% tme$pNum)
```

## Cluster the neighborhoods into distinct LMA types

Using the clusterNeighborhoods function in */COEUR/Scripts/Neighborhood Analysis/SPIAT_functions.R*. **add methods for neighborhood detection**

```{r, message=FALSE}
source("/Users/karanvir/Documents/LMAProject/COEUR/Scripts/Neighborhood Analysis/SPIAT_functions.R")
btLMAs <- clusterNeighborhoods(btNeighborhoods, 7)
adaptLMAs <- clusterNeighborhoods(adaptNeighborhoods, 7)
```

# Visualize composition of each LMA type

## BT Panel

**Figure 1a**

```{r}
getClusterPlots(btLMAs, breaks = c("CD3pCD8n", "CD3pCD8p", "CD79ApCD20n", "CD20p", "CD3pCD8nFoxP3p", "CD3pCD8pFoxP3p"), cell_type_colors = c("#377EB8",
                                "#E41A1C",
                                "#4DAF4A",
                                "#FF7F00",
                                "#FFFF33",
                                "#F781BF"))
```

Renaming LMAs for easier interpretation - LMA1 is mostly **B cells** (B1), LMA7-2-6 have similar compositions **(mostly T cells)**, with decreasing CD8+ and increasing CD8- proportions (T1,T2,T3). LMA5-4-3 are mostly **plasma cell** dominated with increasing proportions of plasma cells (P1,P2,P3).

**Figure 1b**

```{r}
btLMAs$LMA <- recode_factor(btLMAs$LMA, `7`="T1", `2`="T2", `6`="T3", `5`="P1", `4`="P2", `3`="P3", `1`="B1")

getClusterPlots(btLMAs, breaks = c("CD3pCD8n", "CD3pCD8p", "CD79ApCD20n", "CD20p", "CD3pCD8nFoxP3p", "CD3pCD8pFoxP3p"), cell_type_colors = c("#377EB8",
                                "#E41A1C",
                                "#4DAF4A",
                                "#FF7F00",
                                "#FFFF33",
                                "#F781BF"))
```

## ADAPT Panel

**Figure 2a**

```{r}
getClusterPlots(adaptLMAs, breaks =  c("CD68pPDL1n", "CD68pPDL1p", "CD3pCD8pPD1n", "CD3pCD8pPD1p", "CD3pCD8nPD1n", "CD3pCD8nPD1p"), cell_type_colors = c("#4DAF4A",
              "#FFFF33",
              
              "#f4a3a5",
              "#e41a1d",
              "#afcbe3",
              "#377eb8"))
```

Renaming LMA1-LMA6-LMA2-4 to **M1-M2-M3-M4**. LMA7-3-5 to **T1-T2-T3**

**Figure 2b**

```{r}
adaptLMAs$LMA <- recode_factor(adaptLMAs$LMA, `1`="M1", `6`="M2", `2`="M3", `4`="M4", `7`="T1", `3`="T2", `5`="T3")
getClusterPlots(adaptLMAs, breaks =  c("CD68pPDL1n", "CD68pPDL1p", "CD3pCD8pPD1n", "CD3pCD8pPD1p", "CD3pCD8nPD1n", "CD3pCD8nPD1p"), cell_type_colors = c("#4DAF4A",
              "#FFFF33",
              
              "#f4a3a5",
              "#e41a1d",
              "#afcbe3",
              "#377eb8"))
```

# TME-LMA relationship

How many communities of each type do I find in cases of each TME?

BT Panel:

```{r}
btLMAs <- left_join(btLMAs, countsbt %>% select(Image, pNum)) %>% left_join(., tme %>% select(pNum, TME))

btLMAs %>% group_by(TME, LMA) %>% count() %>%
  ggplot(aes(x=TME, y=n, fill=LMA))+
  geom_col(position = position_dodge())+
  scale_fill_npg()+
  ggtitle("Figure 3: Number of LMAs by TME (BT)")+
  theme_minimal()+
  xlab("TME")+
  ylab("# of LMAs")
```

ADAPT panel:

```{r}
adaptLMAs <- left_join(adaptLMAs, countsadapt %>% select(Image, pNum)) %>% left_join(., tme %>% select(pNum, TME))

adaptLMAs %>% group_by(TME, LMA) %>% count() %>%
  ggplot(aes(x=TME, y=n, fill=LMA))+
  geom_col(position = position_dodge())+
  scale_fill_npg()+
  ggtitle("Figure 4: Number of LMAs by TME (ADAPT)")+
  theme_minimal()+
  xlab("TME")+
  ylab("# of LMAs")
```

# Stroma percentage and LMAs

How are percentage of stroma in an image and the \# of LMAs of each type detected correlated? I hypothesize that all types of LMAs should be positively correlated with higher stroma since immune cell density is higher in stroma.

```{r, message=FALSE}
btLMA_matrix <- btLMAs %>% group_by(pNum, LMA) %>% summarise(numberOfLMAs = n()) %>%
  left_join(., tme %>% select(pNum, TME)) %>%
  left_join(., stroma_information) %>%
  pivot_wider(names_from=LMA, values_from = numberOfLMAs, values_fill = 0) %>%
  ungroup() %>%
  select(-pNum, -TME)

btLMA_matrix <- btLMA_matrix %>% select(T1, T2, T3, P1, P2, P3, B1, avg_epi_prop) %>%
  rename("Epithelium prop." = avg_epi_prop)

bt_lma_epi_cor <- cor_mat(btLMA_matrix, vars = names(btLMA_matrix))

rstatix::cor_plot(bt_lma_epi_cor)
```

```{r}
adaptLMA_matrix <- adaptLMAs %>% group_by(pNum, LMA) %>% summarise(numberOfLMAs = n()) %>%
  left_join(., tme %>% select(pNum, TME)) %>%
  left_join(., stroma_information) %>%
  pivot_wider(names_from=LMA, values_from = numberOfLMAs, values_fill = 0) %>%
  ungroup() %>%
  select(-pNum, -TME)

adaptLMA_matrix <- adaptLMA_matrix  %>%
  rename("Epithelium prop." = avg_epi_prop)

adapt_lma_epi_cor <- cor_mat(adaptLMA_matrix, vars = names(adaptLMA_matrix))

rstatix::cor_plot(adapt_lma_epi_cor)
```

Epithelium proportion negatively correlated with all LMA subtypes, except for M1 (PDL1+ macs).

Occurence of each LMA type in high versus low epithelium cases (split at the median). There are 981 total cases - half low, half high epithelium. Out of the 981 cases, *630 have an LMA detected in the adaptive panel, while only 346 have an LMA detected in the BT panel.*

First - how are high and low epithelium cases distributed across the 5 TME?

```{r}
stroma_information <- stroma_information %>% mutate(EPI_BINARY = case_when(avg_epi_prop >= median(avg_epi_prop) ~ "HIGH",
                                      TRUE ~ "LOW"))

left_join(tme, stroma_information) %>% ggplot(aes(x=TME, fill=EPI_BINARY))+
  geom_bar(position=position_dodge())+
  ylab("Number of cases")+
  theme_minimal()+
  ggtitle("Figure 5: Cases stratified by TME and epithelium proportion (n=981)")+
  scale_fill_manual(name="Epithelium proportion", values = (pal_npg()(2)))
```

*Most TME5 cases (hot) are high epithelium*

Now, out of all the LMAs detected, how many are in high versus low epithelium cases? I am visualizing this two ways: 1. The total number of LMAs of each type detected in high and low epi cases. 2. Only considering whether that LMA type was detected in a case at all (presence/absence).

```{r}
bt_stroma <- btLMAs %>% group_by(pNum, LMA) %>% summarise(numberOfLMAs = n()) %>%
  left_join(., tme) %>%
  left_join(., stroma_information) %>%
  group_by(EPI_BINARY, LMA) %>% summarise(sumLMAs = sum(numberOfLMAs))

bt_stroma %>% ggplot(aes(x=LMA, y=sumLMAs, fill=EPI_BINARY)) +
  geom_col(position=position_dodge())+
  scale_fill_npg(name="Epithelium proportion")+
  ggtitle("Fig. 6: Total numbers of LMAs detected by epithelium proportion", subtitle = "BT")

bt_stroma_binary <- btLMAs %>% group_by(pNum, LMA) %>% summarise(numberOfLMAs = n()) %>%
  left_join(., tme) %>%
  left_join(., stroma_information) %>%
  group_by(EPI_BINARY, LMA) %>% count()

bt_stroma_binary %>% ggplot(aes(x=LMA, y=n, fill=EPI_BINARY))+
  geom_col(position=position_dodge())+
   scale_fill_npg(name="Epithelium proportion")+
  ggtitle("Fig 7: Cases with an LMA by epithelium proportion", subtitle="BT")
```

Regardless of how I analyze the data (total number of LMAs versus presence or absence), most occurences of each LMA type are in high stroma cases.

Now looking at the adaptive (macrophage) panel:

```{r, message=FALSE}
adapt_stroma <- adaptLMAs %>% group_by(pNum, LMA) %>% summarise(numberOfLMAs = n()) %>%
    left_join(., tme) %>%
  left_join(., stroma_information) %>%
  group_by(EPI_BINARY, LMA) %>% summarise(sumLMAs = sum(numberOfLMAs))

adapt_stroma %>% ggplot(aes(x=LMA, y=sumLMAs, fill=EPI_BINARY)) +
  geom_col(position=position_dodge())+
  scale_fill_npg(name="Epithelium proportion")+
    theme_minimal()+
  ggtitle("Fig. 8: Total numbers of LMAs detected by epithelium category", subtitle="ADAPT")

adapt_stroma_binary <- adaptLMAs %>% group_by(pNum, LMA) %>% summarise(numberOfLMAs = n()) %>%
      left_join(., tme) %>%
  left_join(., stroma_information) %>%
  group_by(EPI_BINARY, LMA) %>% count()

adapt_stroma_binary %>% ggplot(aes(x=LMA, y=n, fill=EPI_BINARY)) +
  geom_col(position=position_dodge())+
   scale_fill_npg(name="Epithelium proportion")+
  theme_minimal()+
  ggtitle("Fig. 9: Cases with an LMA by epithelium", subtitle="ADAPT")
```

Across the board, the ratio of LMAs in high versus low stroma cases favours high stroma - except for M1, where most of the neighborhoods detected are in low stroma cases (more PDL1 macrophage neighborhoods in low stroma cases).

# Stroma percentage and LMAs - TME5 specific

Maybe there are trends between LMA and stroma proportion that are being masked by the differences in immune infiltration across the 981 cases. If I restrict my analysis to just TME5, are there differences in the occurence of each LMA type between high and low stroma HOT cases?

```{r}
adapt_tme5_stroma <- adaptLMAs %>% group_by(pNum, LMA) %>% summarise(numberOfLMAs = n()) %>%
 left_join(., tme) %>%
  left_join(., stroma_information) %>%
  group_by(TME, EPI_BINARY, LMA) %>% count() %>% 
  filter(TME == 5)

tme_str_tally <- left_join(tme, stroma_information) %>%
  group_by(TME, EPI_BINARY) %>% summarise(n_cases = n())

adapt_tme5_stroma <- adapt_tme5_stroma %>% left_join(tme_str_tally)
adapt_tme5_stroma <- adapt_tme5_stroma %>% mutate(proportion = n/n_cases)

adapt_tme5_stroma %>% ggplot(aes(x=LMA, y=proportion, fill=EPI_BINARY))+
  geom_col(position=position_dodge())+
  scale_fill_npg(name="Epithelium proportion")+
  theme_minimal()+
  ggtitle("Fig. 10: Proportion of total cases in TME5 with a detected LMA", subtitle="ADAPT")
```

A higher proportion of high epithelium cases have M1 and M2 LMAs (in TME5), and less M3 LMAs.

```{r}
bt_tme5_stroma <- btLMAs %>% group_by(pNum, LMA) %>% summarise(numberOfLMAs = n()) %>%
 left_join(., tme) %>%
  left_join(., stroma_information) %>%
  group_by(TME, EPI_BINARY, LMA) %>% count() %>% 
  filter(TME == 5)

bt_tme5_stroma <- bt_tme5_stroma %>% left_join(tme_str_tally)
bt_tme5_stroma <- bt_tme5_stroma %>% mutate(proportion = n/n_cases)

bt_tme5_stroma %>% ggplot(aes(x=LMA, y=proportion, fill=EPI_BINARY))+
  geom_col(position=position_dodge())+
  scale_fill_npg(name="Epithelium proportion")+
  theme_minimal()+
  ggtitle("Fig. 11: Proportion of total cases in TME5 with a detected LMA", subtitle="BT")
```

Expanding the last two plots to look at ALL 5 TMEs.

```{r}
adapt_tme_stroma <- adaptLMAs %>% group_by(pNum, LMA) %>% summarise(numberOfLMAs = n()) %>%
  left_join(., tme) %>%
  left_join(., stroma_information) %>%
  group_by(TME, EPI_BINARY, LMA) %>% count()

adapt_tme_stroma <- adapt_tme_stroma %>% left_join(tme_str_tally)
adapt_tme_stroma <- adapt_tme_stroma %>% mutate(proportion = n/n_cases)

adapt_tme_stroma %>% ggplot(aes(x=LMA, y=proportion, fill=EPI_BINARY))+
  geom_col(position=position_dodge())+
    scale_fill_npg(name="Epithelium proportion")+
  theme_minimal()+
  ylab("Proportion of HGSC cases with a detected LMA")+
  facet_wrap(~TME, ncol=5)+
  coord_flip()+
  theme(legend.position = "bottom")+
  ggtitle("Fig.13: Proportion of total cases in TME1-5 with a detected LMA", subtitle="ADAPT")
```

```{r}
bt_tme_stroma <- btLMAs %>% group_by(pNum, LMA) %>% summarise(numberOfLMAs = n()) %>%
  left_join(., tme) %>%
  left_join(., stroma_information) %>%
  group_by(TME, EPI_BINARY, LMA) %>% count()

bt_tme_stroma <- bt_tme_stroma %>% left_join(tme_str_tally)
bt_tme_stroma <- bt_tme_stroma %>% mutate(proportion = n/n_cases)

bt_tme_stroma %>% ggplot(aes(x=LMA, y=proportion, fill=EPI_BINARY))+
  geom_col(position=position_dodge())+
    scale_fill_npg(name="Epithelium proportion")+
  theme_minimal()+
  ylab("Proportion of HGSC cases with a detected LMA")+
  facet_wrap(~TME, ncol=5)+
  coord_flip()+
  theme(legend.position = "bottom")+
  ggtitle("Fig.14: Proportion of total cases in TME1-5 with a detected LMA", subtitle="ADAPT")
```
