---
title: "IROC Whole Slide LMAs"

format:
  html:
    code-fold: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
library(tidyverse)
library(ggsci)
library(cowplot)
library(ggpubr)
library(rstatix)
source("/Users/karanvir/Documents/LMAProject/COEUR/Scripts/Neighborhood Analysis/SPIAT_functions.R")
```

Exploring LMAs in IROC whole slides.

# Summary statistics

I have data from 23 different IROC patients. The max ROIs captured is 15, the minimum is 5.

```{r}
cellLevel <- vroom::vroom("~/Documents/LMAProject/IROC_WHOLE_SLIDES/raw_data/07Jun23_clean_cell_level.tsv.gz")

cellLevel$Patient <- stringr::str_split_i(cellLevel$Image, "_", 1)

n_images <- cellLevel %>% group_by(Patient) %>% summarise(n_images = length(unique(Image))) %>%
  arrange(n_images)

n_images$Patient <- fct_relevel(n_images$Patient, n_images$Patient)

n_images %>% ggplot(aes(x=Patient, y=n_images))+
  geom_col()+
  coord_flip()+
  xlab("Number of images")+
  cowplot::theme_cowplot()
```

Comparing 7 LMAs in whole slides to 7 LMAs in IROC TMAs.

```{r}
load("/Users/karanvir/Documents/LMAProject/IROC_WHOLE_SLIDES/results/spiat/rdata/IROC_WS_15r_15n_SPIAT.RData")
neighborhoods_df <- bind_rows(neighborhoods, .id = "Image")

clustered <- clusterNeighborhoods(neighborhoods_df, 7)

# Changing order of clusters based on resemblance to TMA LMAs
clustered$LMA <- factor(as.character(clustered$LMA))
clustered$LMA <- fct_relevel(clustered$LMA, "4","3","1","2","7","6","5")

barplots_ws <- getClusterPlots(clustered, breaks = c("CD3pCD8nPD1p", "CD3pCD8nPD1n", "CD3pCD8pPD1p", "CD3pCD8pPD1n", "CD68pPDL1n", 
"CD68pPDL1p", "CD79ApCD20p", "CD79ApCD20n",  "CD3nPD1p"), cell_type_colors = c("#E64B35FF",
                                                                                   "#f5b8af",
                                                                                   "#358295",
                                                                                   "#a6ddea",
                                                                                   "green",
                                                                                   "yellow",
                                                                                   "#744960",
                                                                                   "#d4a2bc",
                                                                                   "black"))
```

```{r}
load("/Users/karanvir/Documents/LMAProject/IROC_TMA/Results/Neighborhood-analysis/RData/IROCTMA_15r_15n_SPIAT.RData")
neighborhoods_tma_df <- bind_rows(neighborhoods, .id = "Image")

clustered_tma <- clusterNeighborhoods(neighborhoods_tma_df, 7)

barplots_tma <- getClusterPlots(clustered_tma, breaks = c("CD3pCD8nPD1p", "CD3pCD8nPD1n", "CD3pCD8pPD1p", "CD3pCD8pPD1n", "CD68pPDL1n", 
"CD68pPDL1p", "CD20p", "CD79ApCD20n",  "PD1p"), cell_type_colors = c("#E64B35FF",
                                                                                   "#f5b8af",
                                                                                   "#358295",
                                                                                   "#a6ddea",
                                                                                   "green",
                                                                                   "yellow",
                                                                                   "#744960",
                                                                                   "#d4a2bc",
                                                                                   "black"))
```

```{r, out.height="200%", out.width="100%"}
ggpubr::ggarrange(barplots_ws, barplots_tma, nrow=2)
```

I can compare the proportions of each LMA to each other by running Analysis of Similarities (ANOSIM) between pairs of LMAs. A score close to 1 indicates dissimilarities in composition, while a score close to 0 indicates that composition of species (ie. cell types) between the two is similar.

```{r, eval=FALSE}

# Analysis of similarities, pairwise between group1 and each of group2

pairwiseANOSIM <- function(group1, group2=c("1","2","3","4","5","6","7")) {
  wholeSlide <- clustered %>% filter(LMA == {{group1}}) %>% select(-Image, -LMA, -Neighborhood) %>% mutate(Group = "WS")
  
  pairwise_results <- lapply(group2, function(x){
     TMA <- clustered_tma %>% filter(LMA == {{x}}) %>% mutate(Group = "TMA") %>% select(-Image, -LMA, -Neighborhood) %>% mutate(Group = "TMA")
  
  test_matrix <- bind_rows(wholeSlide, TMA)
  grouping_var <- test_matrix$Group
  test_matrix <- test_matrix[,1:9] %>% as.matrix()
  test_matrix_prop <- t(apply(test_matrix,1, function(x) x/sum(x)))
  anosim_output <- vegan::anosim(test_matrix_prop, grouping = grouping_var, distance = "bray", permutations = 999)
  
  anosim_summary <- data.frame(WS_LMA = group1,
                               TMA_LMA = group2,
                               ANOSIM = anosim_output$statistic,
                               p = anosim_output$signif)
  })
  
  pairwise_results_df <- bind_rows(pairwise_results)
}


# Need to make sure phenotypes match
clustered_tma <- clustered_tma %>% dplyr::rename(CD79ApCD20p = "CD20p",
                                          CD3nPD1p = "PD1p")

# Running the pairwiseANOSIM function for LMAs 1:7 for the WS
ANOSIMresults <- lapply(c("1", "2", "3", "4", "5", "6", "7"), pairwiseANOSIM)
```
